The Companion Mass Distribution to the ELM WD Sample

### 2014-10-08 documents/letter/ms.tex
Updated .tex

%\documentclass{emulateapj}
\documentclass[letterpaper,12pt,preprint]{aastex}

@@

% commands
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transpose}[1]{{#1}^{\mathsf{T}}}
\newcommand{\inverse}[1]{{#1}^{-1}}
\newcommand{\Msun}{\mathrm{M}_\odot}
\newcommand{\bs}[1]{\boldsymbol{#1}}

@@

\begin{abstract}
Determining component masses of single-line spectroscopic binary stars
is impossible because of the unknown inclination angle. Even when the
mass of the bright star can be derived, only a lower limit can be placed
on the mass of the unseen companion. However, since the probability of
any inclination angle scales with sin $i$, for a large enough, unbiased
population, the companion mass distribution can be deconvolved from the
inclination angle. We develop a Bayesian technique to handle this
deconvolution and place it within a Markov Chain Monte Carlo framework.
We then apply our method to the sample of 55 extremely low mass (ELM)
WDs with radial velocity variations. Modeling the companion mass
distribution as a Gaussian with a variable neutron star component, we
find the companion population is well modeled by a mean of 0.65 and a
standard deviation of 0.3 . Our model indicates a neutron star (NS)
fraction of 1.4$\substack{+7.0 \\ -1.4}$\%.
\end{abstract}

@@

With 55 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the ELM sample is large enough to be statistically modeled. Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased. In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses? 2.\ How many NSs does our simplistic model imply? 3.\ Can we determine the improved likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model? 4.\ Are the six systems without detected radial velocity variations consistent with the population as a whole, or are these a fundamentally separate population (i.e. single ELM WDs)? 5.\ Can our model place limits on the space density of ELM WD binaries with NS companions?

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[angle=90,width=0.7\columnwidth]{Porb_M1.eps}
\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample. The three eclipsing systems, with known $M_2$ are shown by the filled circles. Arrows indicate the masses of ELM WDs without detected radial velocity variation. Triangles indicate the positions of the known WD-NS binaries. From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
\end{center}
\end{figure}

@@

We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}). We would like to find posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$. Using Bayes' rule,
\begin{equation}
    p(\bs{\theta} \given m_f) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
\end{equation}
where $p(m_f \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data. The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
\begin{equation}
    p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
\end{equation}
where we neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles, $i$, are isotropically distributed
\begin{align}
	p(m_f \given M_1, M_2, i) &= \delta(m_f - f(M_1, M_2, i))\\
	f(M_1, M_2, i) &= \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}\\
	p(i) &= \sin i.
\end{align}
For now, we keep this general by not yet specifying a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is
\begin{align}
    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~ \delta(m_f - f(M_1, M_2, i))~\sin i\\
    &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~\sin i ~ \delta(g(M_1,M_2,i))\label{eq:delta}
\end{align}
where
\begin{equation}
	g(M_1,M_2,i) = \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i - m_f.
\end{equation}
The inner integral (over $i$) has the form
\begin{equation}
    \int dx~F(x)~\delta{(G(x)}) = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|}
\end{equation}
where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in Equation~\ref{eq:delta} are 
\begin{align}
	i^* &= \sin^{-1}\alpha\\
	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
\end{align}
With this in mind, we may write the marginal likelihood as
\begin{align}
	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{\sin i^*}{g'(M_1,M_2,i^*)}\\
	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\label{eq:fullm2}
\end{align}
where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$.

@@

We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$. For all experiments -- including that with the real data -- we use a two component Gaussian mixture model to fit the data. However, in tests below, we generate test data with a variety of mixture component forms. We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,1.4)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1,2)~\Msun$. The likelihood with a Gaussian mixture model is
\begin{align}
	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - (m_f(M_1+M_2)^2)^{2/3}}}\\
	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,(0.2 < M_2 < 1.4~\Msun) \\
	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\,(1.4 < M_2 < 2~\Msun)
\end{align}
where $\mathcal{N}$ is the (truncated, but normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified. In this work, we fix the mean and variance of the neutron star distribution to
\begin{align}
	\mu_{\rm NS} &= 1.4~\Msun\\
	\sigma^2_{\rm NS} &= (0.1~\Msun)^2
\end{align}
given the uncertainties in neutron star mass, birth channels, and mass accretion scenarios \citep{refs} [TODO: Jeff, references]. Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$.

We choose standard priors on these parameters. For the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$. We use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2.~\Msun$. We use a uniform distribution over the dimensionless neutron star fraction from $0-1$. The model parameters are summarized in Table~\ref{tbl:parameters}.

\begin{table*}[ht]
\begin{center}
	\begin{tabular}{l c c l} \toprule
		Parameter & Prior \\\toprule
		$f_{\rm NS}$ & $\mathcal{U}(0, 1)$ \\ 
		$\mu_{\rm WD}$ & $\mathcal{U}(0.2, 1.4)$ \\ 
		$\sigma_{\rm WD}$ & $\frac{1}{\ln(40)\sigma}$ $(0.05 < \sigma < 2~\Msun)$ \\ 
		$\mu_{\rm NS}$ & 1.4~$\Msun$ (fixed) \\ 
		$\sigma_{\rm NS}$ &  0.1~$\Msun$ (fixed) \\
		\bottomrule
		\end{tabular}
	\caption{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}. $\mathcal{U}$ is the uniform distribution. There are 3 free parameters. \label{tbl:parameters}}
\end{center}
\end{table*}

@@

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[angle=90,width=1\columnwidth]{model_post.eps}
\caption{Replace this text with your caption}
\label{fig:tests}
\end{center}
\end{figure}

@@

The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, providing precise measurements for $P_{\rm orb}$ and $K$. Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$. We use the spectroscopic solutions found in \citet{Gianninas14}. Furthermore, three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$, J0651$+$2844: $M_2=0.50~\Msun$, and J0751$-$0141: $M_2=0.97~\Msun$). These are taken into account in our model through equation {\bf XXX}. Since the inclination angle cannot vary, these systems will strongly affect the likelihood of any particular model.

Finally, six systems in the ELM WD sample lack radial velocity variations, with upper limits of $\approx$20-50 km s$^{-1}$. Some of these may be in binaries with radial velocities below the detection limit, due to low inclination angle, however studies by {\bf XXX} suggest there may also be a population of single LMWDs. Because of the uncertainty in their formation, we restrict these from our sample.

%In principle we could add to our model the possibility that each of these WDs is actually a single ELM WD. Because this requires an additional six free parameters, one for each ELM WD without radial velocity variations, including these in our model becomes too computationally expensive.

%We apply our model to the ELM WD data set, using 10 independent Markov chains, each run for 100,000 steps. The acceptance fraction is {\bf XXX}. We determine an autocorrelation length of {\bf XXX} steps, and correspondingly, only include every {\bf XXX} samples for our posterior distributions. {\bf Is there anything else we need to say about the applying the method to the data set?}

The results of our model are shown in Figure \ref{fig:ELM_post}. The first panel shows the distribution of $M_{2,min}$ for the data set, showing a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$. The second panel shows the posterior distribution of $\mu$ and $\sigma$; contours indicate 1, 2, and 3-$\sigma$ confidence levels. The best fit Gaussian model has a mean of 0.66 $\substack{+0.12 \\ -0.09}~\Msun$ and a standard deviation of 0.27$\substack{+0.09 \\ -0.07}~\Msun$. The third panel shows the NS fraction is strongly peaked toward low probabilities. Our model indicates a NS fraction of 1.4$\substack{+7.0 \\ -1.4}$\% at the 68\% confidence level, however there is a non-negligible tail toward higher NS probabilities. This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows a histogram of NS probabilities for individual systems. These probabilities are obtained by taking the average of the posterior distribution of NS probabilities for each system. Although a few systems have high probabilities, the distribution is strongly clustered below 20\%.

@@

Our results indicate that the best fit Gaussian for the companions to the ELM WD sample is very similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}. However, our distribution is significantly wider ($\sigma \approx 0.3~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well. Furthermore, population synthesis predictions suggest there may be two distinct companion populations to LMWD, composed of both CO and He core WDs. The ratio of these two populations depends on the exact stellar evolution prescriptions assumed \citep{toonen12}. Our method here could be extended to include multiple Gaussians with varying weights, however adding only one more Gaussian component doubles the number of free parameters from three to six. Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines. In principle, the ratio of He+He to He+CO WD systems could be determined using two Gaussian model, potentially placing an important constraint on population synthesis models. It remains to be seen whether such a model can place such constraints with 55 measured systems. We plan to explore this in a future work, however it may require a larger data set.

There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve. However, the posterior distribution in $\mu$ and $\sigma$ is well behaved, with a clear high probability region, similar to the posterior distributions for $\mu$ and $\sigma$ for our first two test cases shown in Figure \ref{fig:ELM_post}. The part of the distribution with a low $\mu$ and high $\sigma$ is indicative of a low mass WD component.

Systems with NS companions cannot be differentiated from those with WD companions through orbital period and ELM WD mass alone. Our model attempts to determine a NS fraction for the population as a whole. This is an improvement over NS probabilities for individual companions calculated through Equation \ref{P_NS_approx}. The third panel in Figure \ref{fig:ELM_post} indicates a NS fraction of a few percent. For 55 systems with observed radial velocity variations, this corresponds to a 1-2 systems with NS companions. However, the top left panel in Figure \ref{fig:tests} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass wing of our Gaussian distribution. It is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions. Nevertheless, our model indicates a NS fraction of {\bf XXX\%}, corresponding to zero to four systems.

If we combine our result of a NS fraction of {\bf XXX} with the ELM WD space density as determined from the Palomar Green Survey: $4\times10^{-14}$pc$^{-3}$yr$^{-1}$ \cite{liebert05} {\bf Is there a more recent estimate?} we can get a space density of ELM WD + NS binaries. This suggests that there are {\bf XXX} such binaries within a few kpc of us. Compare to the number of known MSP+LMWDs.

The fourth panel in Figure {\bf XXX} shows  that only two systems have $P(NS)$ above 25\%: J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%). These systems are ideal candidates for searches for NS companions in radio and X-ray. Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, even if this system is a NS, it may not be detectable in radio. However, all NS give off blackbody radiation as X-rays, and X-ray follow-up provides a more stringent test on the potential for a NS companion.

\begin{figure}[h!]
\begin{center}
\includegraphics[angle=90,width=1\columnwidth]{ELM_post.eps}
\caption{Replace this text with your caption}
\label{fig:ELM_post}
\end{center}
\end{figure}

\subsection{Non-detections}

Six systems in the ELM WD sample have non-detections of companions, down to an upper limit on the transverse velocity. We include these systems in our model, too, as in principle they could be binary systems at with low inclination angles or long period orbits or both. We can estimate the number of binaries with inclination angles too low to produce observable radial velocity variations:

\begin{equation}
P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} \int_0^{i_{\rm max}} P(M_2|\mathbf{\Theta})\ {\rm sin}\ i\ {\rm d}i\ {\rm d}M_2
\end{equation}

which reduces to:

\begin{equation}
P(K<K_{\rm max} | \mathbf{\Theta}) = \int_0^{\infty} P(M_2|\mathbf{\Theta})\ \left( 1 - {\rm cos}\ i_{\rm max}\right)\ {\rm d}M_2
\end{equation}

>>>>

\documentclass[apjl]{emulateapj}
%\documentclass[letterpaper,12pt,preprint]{aastex}

@@

% commands
\newcommand{\given}{\,|\,}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\transpose}[1]{{#1}^{\mathsf{T}}}
\newcommand{\inverse}[1]{{#1}^{-1}}
\newcommand{\Msun}{\ifmmode {{\rm M}_{\odot}}\else M$_{\odot}$\fi}
\newcommand{\bs}[1]{\boldsymbol{#1}}

@@

\begin{abstract}
Determining component masses of single-line spectroscopic binary stars
is impossible because of the unknown inclination angle. Even when the
mass of the bright star can be derived, only a lower limit can be placed
on the mass of the unseen companion. However since the probability of
any inclination angle scales with sin $i$, for a large enough, unbiased
sample, the companion mass distribution can be deconvolved from the
inclination angle distribution. We develop a Bayesian technique to handle this
deconvolution and place it within a Markov Chain Monte Carlo framework.
We then apply our method to the sample of 55 extremely low mass (ELM)
WDs with radial velocity variations. Modeling the companion mass
distribution as a Gaussian with a variable neutron star component, we
find the companion population is well modeled by a mean of 0.74 \Msun\ and a
standard deviation of 0.26 \Msun. Our model indicates a neutron star (NS)
fraction of 1.4$\substack{+7.0 \\ -1.4}$\%.
\end{abstract}

@@

With 55 systems with precise $M_1$, $P_{\rm orb}$, and $K$, the ELM sample is large enough to be statistically modeled. Furthermore, since the population was selected based on characteristics determined by the primary mass alone, at least with regard to the inclination angle and companion mass, the population is unbiased. In this work we develop a model to determine the mass distribution of companions to ELM WDs in an attempt to answer several specific scientific questions: 1.\ Can the population as a whole be modeled using a simple description of the companion masses? 2.\ What is the rate of NS implied by our model? 3.\ Can we improve the likelihood of any individual system having a NS companion, taking into account the overall rate of NS's in the sample implied by our model?

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[angle=90,width=0.95\columnwidth]{Porb_M1.eps}
\caption{The $P_{\rm orb}$ - $M_1$ distribution of the ELM WD sample. The three eclipsing systems, with known $M_2$ are shown by the filled circles. Arrows indicate the masses of ELM WDs without detected radial velocity variation. Triangles indicate the positions of the known WD-NS binaries. From $P_{\rm orb}$ and $M_1$ alone, the two populations are indistinguishable.}
\end{center}
\end{figure}

@@

We construct a statistical model to derive constraints on a parametric model for the distribution of ELM WD companion masses, $p(M_2 \given \bs{\theta})$.\footnote{In what follows, vectors or sets of parameters or quantites are represented by bold symbols.} For each system, we assume we are given $K$, $T$, and $M_1$ and therefore know the value of the mass function, $m_f$ (Eq.~\ref{eq:massfunc}). We would like to find posterior constraints on the parameters, $\bs{\theta}$, that describe the distribution of companion masses, $p(M_2\given \bs{\theta})$, given all of the observed mass functions, $\bs{m}_f$, by deconvolving the distribution of mass functions from the unobserved inclination angle, $i$. Using Bayes' rule,
\begin{equation}
    p(\bs{\theta} \given m_f) = \frac{1}{\mathcal{Z}}~p(m_f \given \bs{\theta})~p(\bs{\theta}).
\end{equation}
where $p(m_f \given \bs{\theta})$ is the likelihood, $p(\bs{\theta})$ is the prior on parameters $\bs{\theta}$, and the evidence integral, $\mathcal{Z}$, is a constant that depends only on the data. The marginal likelihood, $p(m_f \given \bs{\theta})$, involves integrals over the latent variables $i$ and companion mass, $M_2$,
\begin{equation}
    p(m_f \given \bs{\theta}) = \int_0^{\pi/2} di \int_{-\infty}^\infty dM_2~p(m_f \given M_1, M_2, i)~p(M_2 \given \bs{\theta})~p(i).
\end{equation}
where we neglect observational uncertainties in the mass function,\footnote{This is justified because the relative uncertainties in these quantities are small, $\sigma_x / x \sim 0.1$, however in future work we will extend this methodology to include uncertainties in all measured quantities.} and assume the inclination angles, $i$, are isotropically distributed
\begin{align}
	p(m_f \given M_1, M_2, i) &= \delta \left[m_f - f(M_1, M_2, i) \right]\\
	f(M_1, M_2, i) &= \frac{(M_2 \sin i)^3}{(M_1 + M_2)^2}\\
	p(i) &= \sin i.
\end{align}
For now, we keep this general by not yet specifying a parametric form for the companion mass distribution, $p(M_2 \given \bs{\theta})$. With the above assumptions, the marginal likelihood integral is
\begin{align}
    p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~ \delta \left[m_f - f(M_1, M_2, i)\right]~\sin i\\
    &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta}) \int_0^{\pi/2} di ~\sin i ~ \delta \left[g(M_1,M_2,i) \right]\label{eq:delta}
\end{align}
where
\begin{equation}
	g(M_1,M_2,i) = \frac{M_2^3}{(M_1+M_2)^2}\sin^3 i - m_f.
\end{equation}
The inner integral (over $i$) has the form
\begin{equation}
    \int dx~F(x)~\delta{(G(x)}) = \sum_j \frac{F(x^*_j)}{|G'(x^*_j)|}
\end{equation}
where the sum is over the roots, $x^*_j$, of the function $G(x)$. The root, $i^*$, and derivative of the argument of the delta function in Equation~\ref{eq:delta} are 
\begin{align}
	i^* &= \sin^{-1}\alpha\\
	\alpha &= \frac{(m_f(M_1+M_2)^2)^{1/3}}{M_2}\\
	\frac{\partial g}{\partial i} &= \frac{3M_2^3}{(M_1+M_2)^2}\sin^2 i \cos i\\
	\frac{\partial g}{\partial i}\bigg\rvert_{i^*} &= \frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}
\end{align}
With this in mind, we may write the marginal likelihood as
\begin{align}
	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{\sin i^*}{g'(M_1,M_2,i^*)}\\
	&= \int_{0}^\infty dM_2~p(M_2 \given \bs{\theta})~\alpha\left[\frac{3M_2^3}{(M_1+M_2)^2} \alpha^2 \sqrt{1 - \alpha^2}\right]^{-1}\\
	&= \int_{M_{2,{\rm min}}}^\infty dM_2~p(M_2 \given \bs{\theta})~\frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\label{eq:fullm2}
\end{align}
where the bottom bound in the integral in Equation~\ref{eq:fullm2} is set by the minimum companion mass for which the integrand is real, $M_{2,{\rm min}}$.

@@

We must now choose a functional form for the companion mass distribution,  $p(M_2\given \bs{\theta})$. For all experiments -- including that with the real data -- we use a two component Gaussian mixture model to fit the data. However, in tests below, we generate test data with a variety of mixture component forms. We truncate the distributions using physically motivated bounds so that the white dwarf component is restricted to the range $M_2\in (0.2,1.4)~\Msun$ and the neutron star component is restricted to the range $M_2\in (1,2)~\Msun$. The likelihood with a Gaussian mixture model is
\begin{align}
	h(M_2, m_f, M_1) &= \frac{(M_1+M_2)^{4/3}}{3m_f^{1/3}M_2\sqrt{M_2^2 - \left[ m_f(M_1+M_2)^2 \right]^{2/3}}}\\
	p(m_f \given \bs{\theta}) &= \int_{0}^\infty dM_2~\left[ (1-f_{\rm NS})p_{\rm WD} + f_{\rm NS}p_{\rm NS} \right]~h(M_2, m_f, M_1)\\
	p_{\rm WD} &= \mathcal{N}(M_2 \given \mu_{\rm WD}, \sigma^2_{\rm WD});\,(0.2 < M_2 < 1.4~\Msun) \\
	p_{\rm NS} &= \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS});\,(1.4 < M_2 < 2~\Msun)
\end{align}
where $\mathcal{N}$ is the (truncated, but normalized) normal distribution with mean $\mu$ and variance $\sigma^2$ and the distributions are limited to the ranges specified. In this work, we fix the mean and variance of the neutron star distribution to
\begin{align}
	\mu_{\rm NS} &= 1.4~\Msun\\
	\sigma^2_{\rm NS} &= (0.1~\Msun)^2
\end{align}
given the uncertainties in neutron star mass, birth channels, and mass accretion scenarios \citep{refs} [TODO: Jeff, references].

The probability of any particular system having a NS companion $P({\rm NS})$ is then:

\begin{equation}
P({\rm NS}) = \int_{0}^\infty dM_2~ f_{\rm NS}~ \mathcal{N}(M_2 \given \mu_{\rm NS}, \sigma^2_{\rm NS})~ h(M_2, m_f, M_1) \label{eq:P_NS_full}
\end{equation}

Our companion mass model parameters are then $\bs{\theta} = (\mu_{\rm WD}, \sigma_{\rm WD}, f_{\rm NS})$. We choose standard priors on these parameters. For the mean of the white dwarf component, we use a uniform distribution from $0.2-1.4~\Msun$. We use a (scale-invariant) logarithmic prior for the variance of the white dwarf component over the range $0.05-2.~\Msun$. We use a uniform distribution over the dimensionless neutron star fraction from $0-1$. The model parameters are summarized in Table~\ref{tbl:parameters}.

\begin{table}[ht]
\begin{center}
	\begin{tabular}{l c c l} \toprule
		Parameter & Prior \\\toprule
		$f_{\rm NS}$ & $\mathcal{U}(0, 1)$ \\ 
		$\mu_{\rm WD}$ & $\mathcal{U}(0.2, 1.4)$ \\ 
		$\sigma_{\rm WD}$ & $\frac{1}{\ln(40)\sigma}$ $(0.05 < \sigma < 2~\Msun)$ \\ 
		$\mu_{\rm NS}$ & 1.4~$\Msun$ (fixed) \\ 
		$\sigma_{\rm NS}$ &  0.1~$\Msun$ (fixed) \\
		\bottomrule
		\end{tabular}
	\caption{Parameter information for the form of the companion mass distribution used in the experiments of Section~\ref{sec:experiments}. $\mathcal{U}$ is the uniform distribution. There are 3 free parameters. \label{tbl:parameters}}
\end{center}
\end{table}

@@

\begin{figure*}[h!]
\begin{center}
\includegraphics[angle=90,width=0.95\textwidth]{model_post.eps}
\caption{Replace this text with your caption}
\label{fig:tests}
\end{center}
\end{figure*}

@@

@@

The ELM WD sample is composed of 55 systems with radial velocity variations fit to orbital solutions, providing precise measurements for $P_{\rm orb}$ and $K$. Fits to spectroscopic templates provide high S/N spectra provide precisely determined $M_1$. We use the spectroscopic solutions found in \citet{gianninas14}. Three systems are eclipsing binaries, with known companion masses (J0345$+$1748: $M_2=0.72~\Msun$ \citep{kaplan14}, J0651$+$2844: $M_2=0.50~\Msun$ \citep{brown11b}, and J0751$-$0141: $M_2=0.97~\Msun$ \citep{kilic14}). These are taken into account in our model through equation {\bf XXX}. Furthermore, six systems in the ELM WD sample show no radial velocity variations, with upper limits of $\approx$20-50 km s$^{-1}$. Some of these systems may be in low inclination angle binaries with radial velocities below the detection limit, or have orbital periods near 24 hours, which are difficult to detect \citep{ELMV}. These LMWDs could also have companions at systematically longer orbital periods, with orbital velocities below the detection limit. Because of the uncertainties in their formation, we restrict these from our sample.

The results of our model are shown in Figure \ref{fig:ELM_post}. The first panel shows the distribution of $M_{2,min}$ for the data set, showing a small high mass component, and the majority of sample with $M_{2,min}$ below $0.8~\Msun$. The second panel shows the posterior distribution of $\mu$ and $\sigma$; The maximum a posteriori Gaussian model has a mean of 0.74 \Msun\ and a standard deviation of 0.26 \Msun. The third panel shows a NS fraction strongly peaked toward zero, however there is a non-negligible tail toward higher NS probabilities. This is further indicated by the fourth panel in Figure \ref{fig:ELM_post} which shows a histogram of NS probabilities for individual systems. These probabilities are obtained by taking the average of the posterior distribution of NS probabilities for each system. Although a few systems have high probabilities, the distribution is strongly clustered near 0\%.

@@

There is no reason to expect the true companion mass distribution to ELM WDs follows a Gaussian curve. However, the posterior distribution in $\mu$ and $\sigma$ is strongly peaked, indicating that our naive Gaussian model is a good descriptor of the companion mass distribution. Our results indicate that the best fit Gaussian for the companions to the ELM WD sample is very similar to that of the population of single DA WDs in SDSS with a mean of 0.6 $\Msun$ \citep{kleinman13}. However, our distribution is significantly wider ($\sigma \approx 0.26~\Msun$ compared with $\sigma \approx 0.1~\Msun$), likely due to mass transfer affecting the mass distribution of the unseen primary WDs as well.

Population synthesis predictions suggest there may be two distinct companion populations to LMWD, composed of both CO and He core WDs. The ratio of these two populations depends on the exact stellar evolution prescriptions assumed \citep[see e.g., ][]{toonen12}. In principle, the ratio of He+He to He+CO WD systems could be determined using two Gaussian model, potentially placing an important constraint on population synthesis models. However adding only one more Gaussian component doubles the number of free parameters from three to six. Finding the maximum likelihood in a three dimensional parameter space is computationally expensive, and moving to a six dimensional space may require more complex numerical routines.  It remains to be seen whether constraints can be placed with 55 measured systems using such a model. We plan to explore this in a future work, as well as a comparison with population synthesis models.

While we were writing this work, we became aware of recent high-speed photometric observations by \citet{hermes14}. Although their search was designed to search 20 LMWD systems for eclipses, they placed limits on the maximum inclination angle of these 20 systems based on the non-detection of eclipses. For eight objects they determined the companion mass based on models fitting the observed photometric variability, primarily due on ellipsoidal variation and doppler beaming. Including these observations in our model is non-trivial and remains outside the scope of this work, however we plan to explore this in a future work.

\begin{figure*}[h!]
\begin{center}
\includegraphics[angle=90,width=0.95\textwidth]{ELM_post.eps}
\caption{Replace this text with your caption}
\label{fig:ELM_post}
\end{center}
\end{figure*}

\subsection{NS Companion Probability}

Systems with NS companions cannot be differentiated from those with WD companions through the mass function and LMWD mass alone. Our model attempts to determine a NS fraction for the population as a whole. This is an improvement over NS probabilities for individual companions calculated through Equation \ref{P_NS_approx}. The third panel in Figure \ref{fig:ELM_post} indicates a NS fraction of a few percent. For 55 systems with observed radial velocity variations, this corresponds to a 1-2 systems with NS companions. However, the top left panel in Figure \ref{fig:tests} shows that even a system with $M_{2,min}=1.0~\Msun$ can be a WD from the high mass wing of our Gaussian distribution. It is not guaranteed that any of the LMWDs in the ELM WD sample have NS companions. Nevertheless, our model indicates a NS fraction of {\bf XXX\%}, corresponding to zero to four systems.

The probability of any particular ELM WD having a NS companion will vary depending on the NS fraction of the sample. This is not taken into account in Equation~\ref{eq:P_NS_approx}. When the NS mass is approximated as a delta function, this can be evaluated analytically, $P(NS)$ reduces to calculating $f_{\rm NS} \times h(M_{\rm NS},m_f,M_1)$:

\begin{equation}
P({\rm NS}) = f_{\rm NS} \frac{(M_1+M_{\rm NS})^{4/3}}{3m_f^{1/3}M_{\rm NS}\sqrt{M_{\rm NS}^2 - \left[m_f(M_1+M_{\rm NS})^2 \right]^{2/3}}} \label{eq:P_NS}
\end{equation}

This equation, approximating the NS population as a delta function around $M=1.4$~\Msun\ instead of the full integral around the Gaussian NS distribution defined in Equation~\ref{eq:P_NS_full}, is accurate to $\sim${\bf XXX}\%. We therefore suggest using this equation, combined with the $f_{\rm NS}$ determined here to provide future estimates for the probability of a NS companion to any LMWD system with a measured $m_f$ and $M_1$.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% If we do this calculation, we need to think more about it
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%Combining our resulting NS fraction of {\bf 5\%} with the ELM WD space density of 40 kpc$^{-3}$ as determined by \citet{brown11a}, we can find a space density of ELM WD + NS binaries of 2 kpc$^{-3}$. If we assume an exponential disk with a scale height of 250 pc, this suggests that there are $\approx$  such binaries within a two kpc of us. Compare to the number of known MSP+LMWDs.

The fourth panel in Figure {\bf XXX} shows  that only two systems have $P({\rm NS})$ above 25\%: J0811$+$0225 ({\bf XXX}\%) and J1741$+$6526 ({\bf XXX}\%). These systems are ideal candidates for searches for NS companions in radio and X-ray. Radio observations of these objects are in progress, however because a NS companion may be radio quiet or beamed away from us, even if this system is a NS, it may not be detectable in radio. All NS give off blackbody radiation peaked in X-ray wavelengths, therefore X-ray follow-up provides a more stringent test on the potential for a NS companion. Previous searches for LMWDs with X-ray counterparts have all been non-detections, however we show here that all those sources have a low probability of hosting a NS companion. If J0811$+$0225 and J1741$+$6526 also lack X-ray counterparts, then stringent constraints can be placed on $f_{\rm NS}$. In principle, our model can also include the non-detection of radio and X-rays for those systems in which searches have already been performed. We leave this to a future work.
